CDIPS. I. Light Curves in Open Clusters from TESS Sectors 6 \& 7

### 2019-08-06 paper_I/ms.tex
updated paper
it's beginning to look better (!)

Each of the $\sim$3000 known star clusters of the Milky Way is a gift
to astrophysics, providing a sample of stars that vary widely in mass
but all have approximately the same age and composition.  Time-series
photometry of clusters has many applications. By measuring rotation
periods over a range of ages, we can study the angular momentum
evolution of stars and improve our ability to determine stellar ages
through gyrochronology \citep[{\it
e.g.},][]{skumanich_time_1972,barnes_color-period_2015,meibom_spin-down_2015,curtis_tess_2019}.
By measuring eccenticities as a function age, we can study the tidal
circularization of binaries
\citep{meibom_robust_2005,milliman_wiyn_2014,price-whelan_binary_2018}.
The detection of eclipsing binaries can also lead to the precise
determination of the absolute dimensions of the stars and stringent
tests of stellar-evolutionary models
\citep{luhman_formation_2012,stassun_review_2014,kraus_mass-radius_2015}.
Finally, transiting exoplanets discovered in clusters can shed light
on the timescales for processes in planet formation, evolution, and
migration
\citep[][]{Fortney_et_al_2007,Mann_K2_33b_2016,David_et_al_2017}, as
well as on the effects of metallicity
\citep[][]{fischer_planet-metallicity_2005,petigura_metallicity_2018}.

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{target_star_positions.png}
		%\gridline{\fig{target_star_cumulative_counts.pdf}{0.41\textwidth}{}}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    Target star positions (blue) and predicted TESS observing
    footprint (gray).  Target stars are either candidate members of
    clusters, or else have other youth indicators (see
    \S~\ref{sec:starselection}).  Most will be observed for one or two
    lunar months over the TESS Prime Mission.
    \label{fig:cdips_targets_positions}
	}
\end{figure}

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		%\includegraphics[width=0.45\textwidth]{target_star_cumulative_counts.png}
		\gridline{\fig{target_star_cumulative_counts.pdf}{0.41\textwidth}{}}
		\vspace{-0.8cm}
		\gridline{\fig{target_star_hist_logt.pdf}{0.41\textwidth}{}}
		\vspace{-0.8cm}
		\gridline{\fig{target_star_reference_pie_chart.pdf}{0.41\textwidth}{}}
	\end{center}
	\vspace{-0.8cm}
	\caption{
		Target star statistics.
		{\it Top.} Cumulative counts as a function of Gaia $Rp$-band
		magnitude.  
		{\it Middle.} Histogram of target star ages, for the subset of
		stars with ages matched against \citet{Kharchenko_et_al_2013}.
		{\it Bottom.} Provenance of cluster membership.  Percentages are
		relative to $N_{\rm total}=1061446$ target stars. Symbols
		are as follows.
		D14 is \citet{dias_proper_2014}.
		K13 is \citet{Kharchenko_et_al_2013}.
		CG18 is \citet{cantat-gaudin_gaia_2018}.
		Z18 is \citet{zari_3d_2018}, with upper main sequence and
		pre-main-sequence samples sub-divided.
		``$\geq 2$'' indicates at least two authors reported a star as a
		candidate cluster member.
		%``Other'' refers to sources enumerated in \S~\ref{sec:starselection}.
		\label{fig:cdips_targets}
	}
\end{figure}

\begin{figure*}[!t]
	\gridline{\fig{mwscmatchstats.pdf}{0.75\textwidth}{}}
	\vspace{-0.8cm}
	\gridline{\fig{dias14matchstats.pdf}{0.75\textwidth}{}}
	\vspace{-0.8cm}
	\caption{
		{\it Top.} Quality diagnostics from cross-matching
		\cite{Kharchenko_et_al_2013} cluster members against Gaia-DR2.
		A histogram of the distances between matched stars is on the left; a
		histogram of the difference between the true $G$-band magnitude
		and that predicted from 2MASS photometry is in the middle; a scatter
		plot of the same magnitude difference as a function of $G$-band
		magnitude is on the right.
		{\it Bottom.} Same, but cross-matching \cite{dias_proper_2014}
		cluster members to Gaia-DR2.
	}
	\label{fig:xmatch_info}
\end{figure*}

@@

The resulting CDIPS target star list is given in Table~N.
The cumulative distribution of target star brightnesses, as well as a
histogram of the ages, is shown in Figure~\ref{fig:cdips_targets}.
Relative to field stars, our target star sample is young, with a
typical age of 100$\,$Myr.

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.3\textwidth]{pipelineoverview.pdf}
	\end{center}
	\vspace{-0.2cm}
	\caption{
    Conceptual overview of photometric reduction pipeline.
    Details are given in \S~\ref{sec:method}.
    %TODO: add latex section numbers!
    %TODO: do FORCED aperture photomery on differenced images
    %TODO: improve text generally
	\label{fig:pipeline}
	}
\end{figure}

\begin{figure*}[!t]
    \begin{center}
        \leavevmode
        \includegraphics[width=0.95\textwidth]{stages_of_image_processing_good.png}
    \end{center}
    \vspace{-0.6cm}
    \caption{
        Stages of image processing for an image taken during the middle
        of an orbit.
        {\it Top right}. Calibrated image.
        {\it Top left}. Smooth background estimate.
        {\it Middle right}. Calibrated image minus its median pixel value.
        {\it Middle left}. Calibrated image minus smooth background.
        {\it Bottom left}. Registered difference image.
        {\it Bottom right}. Zoom of difference image.
        Each image is $(2048\times2048)$ pixels, except for the bottom-right 
        image, which is $(500\times500)$.
        All images except the top-right have the same color map.
        The sector, camera, and CCD are (6, 1, 2).
        \label{fig:stages_good}
    }
\end{figure*}

\begin{figure*}[!t]
    \begin{center}
        \leavevmode
        \includegraphics[width=0.95\textwidth]{stages_of_image_processing_bad.png}
    \end{center}
    \vspace{-0.6cm}
    \caption{
        Same sector, camera and CCD as Figure~\ref{fig:stages_good}, but for an image taken during
        perigee passage, when scattered light from the Earth is
        prominent.
        A number of systematic artifacts are present,
        including vertical ``straps'' and small-scale structure in scattered light
        patches.
        The quality of astrometric registration in the difference image is also
        worse, leading to larger residuals in the lower-right panel.
        \label{fig:stages_bad}
    }
\end{figure*}

@@

\begin{figure}[!t]
	\gridline{\fig{astromresidual_hist.pdf}{0.5\textwidth}{}}
	\vspace{-0.8cm}
	\gridline{\fig{astromresidual_quiver.pdf}{0.5\textwidth}{}}
  %\vspace{-0.8cm}
	%\gridline{\fig{astromresidual_apertures.pdf}{0.5\textwidth}{}}
	\vspace{-0.8cm}
    \caption{
		{\it Top.} Histogram of astrometric residual. The $x$-axis shows 
		the distance between the measured centroid positions of stars, 
		compared to the predicted positions from the WCS solution.
		{\it Bottom.} Vector plot of astrometric residual. Each arrow is 
		the vector from the measured to the projected star position. 
		Directions are correct, but lengths are 50 times their true size for 
		visualization purposes.
    The systematic error in the top-right corner is a typical
    problem generic to wide-field astrometry.
    The frame chosen for this plot is the photometric reference frame used 
    for Sector 6, Camera 1, CCD 1; we automatically 
    impose cutoffs on the median and $90^{\rm th}$ percentile of the 
    astrometric residual in order to ensure similar levels of astrometric 
    precision are maintained throughout the reduction.
	}
	\label{fig:astromresid}
\end{figure}

@@

With a kernel selected, and the convolution and subtraction performed,
we calculate the instrumental fluxes for each frame per
Equation~\ref{eq:ism_flux_measurement}.  We did this with three
different aperture sizes: for this work, circles of radii 1 pixel, 1.5
pixels, and 2.25 pixels.  These sizes were chosen to roughly span the
range of optimal aperture sizes for stars in our sample, as calcuated
from the pre-flight \citet{Sullivan_et_al_2015} noise model.  Finally,
to convert from a list of flux measurements for each source on a frame
to a list of flux values at any given time, we used the
\texttt{fitsh} transposition tool \texttt{grcollect}.

@@

To determine the ``optimal'' number of principal components to use, we
performed a cross-validation analysis on the template stars using the
components derived both from PCA, as well as a separate factor
analysis.  As is typically the case when the noise variance is
different for each ``feature'' (each point in time), we found that
$k$-folding cross-validation using PCA failed to recover a plausible
number of components\footnote{See for example
\url{https://scikit-learn.org/stable/auto_examples/decomposition/plot_pca_vs_fa_model_selection.html}}.
However, the factor analysis typically maximized the cross-validation
score with anywhere from $10$ to $15$ components, which agreed with a
visual analysis of the number of PCA components past which overfitting
began.  We therefore used the maximum cross-validation score from
thefactor analysis as the number of principal components to use in
each light curve.  This number is documented in the \texttt{FITS}
header of each light curve.

@@

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{galacticcoords_cluster_field_star_positions.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    Positions of light curves from TESS Sectors 6 and 7 in galactic
    coordinates.  Black: $G_{\rm Rp}<13$ field stars.  Blue: $G_{\rm
    Rp}<16$ target stars.  Target stars are mostly near the galactic
    plane. The data for Sectors 6 and 7 cover about one-sixth of the
    galactic plane.
		\label{fig:lcgalactic}
	}
\end{figure*}

@@

\begin{figure}[!ht]
	\gridline{\fig{hrd_scat_all_CDIPS_LCs.pdf}{0.45\textwidth}{}}
	\vspace{-0.8cm}
	\gridline{\fig{hrd_scat_close_subset.pdf}{0.45\textwidth}{}}
	\vspace{-0.8cm}
	\caption{
    {\it Top.} HR diagram of CDIPS stars on silicon in this data
    release.  {\it Bottom.} HR diagram of close CDIPS stars on
    silicon. The wedge separating the pre-MS sample from the MS stars
    was discussed by \citet{zari_3d_2018}, who introduced it in order
    to avoid contamination by photometric binaries.
	}
	\label{fig:hrd}
\end{figure}

\begin{figure}[!t]
	\gridline{\fig{pm_scat_all_CDIPS_LCs.pdf}{0.45\textwidth}{}}
	\vspace{-0.8cm}
	\gridline{\fig{pm_scat_close_subset.pdf}{0.45\textwidth}{}}
	\vspace{-0.8cm}
	\caption{
		{\it Top.} Proper motions of CDIPS stars on silicon in this
		data release.  Many of the stars in the central ``blob'' are possible
		field-contaminants.
		{\it Bottom.} Proper motions of close CDIPS stars
		on silicon.
	}
	\label{fig:propermotions}
\end{figure}

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.97\textwidth]{IRM-PCA-TFA_rms_vs_mag.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    Standard deviation of CDIPS light curves as a function of catalog
    TESS-band magnitude.  Left-to-right are raw, PCA-detrended, and
    TFA-detrended light curves. Black points correspond to the minimum
    RMS across the available three aperture sizes.  The model (orange
    and gray lines) assumes aperture sizes reported by
    \citet{Sullivan_et_al_2015}, and the effective area from
    \citet{vanderspek_2018}.  The noise from unresolved background
    stars (dotted gray line) is a function of galactic latitude, and
    dominates over zodiacal light for faint stars near the galactic
    plane; the line shown assumes a sight-line towards the center of
    Sector 6, Camera 1 (further details are in
    \S~\ref{subsubsec:rmsvsmag}).
		\label{fig:rms_vs_mag}
	}
\end{figure*}

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.97\textwidth]{avg_acf.pdf}
	\end{center}
	\vspace{-0.5cm}
  \caption{
    Average autocorrelations of $10^4$ randomly selected light curves
    from each sector.  The medians at time lags spaced by one hour are
    shown for raw light curves (column name \texttt{IRM}) in gray, and
    for TFA-detrended light curves in black.  The gray bands display
    the 25$^{\rm th}$ to 75$^{\rm th}$ percentile range for each type
    of light curve.
  \label{fig:avg_acf}
	}
\end{figure*}

\subsection{Light Curve Statistics}
\label{subsec:lcstatistics}

@@

The relevant quantity needed to calculate the integrated 
photon counts from faint sources
is  $N(<m,l,b)$ --- the number of stars per square arcsecond
brighter than magnitude $m$, along a line of sight with galactic
longitude and latitude $(l,b)$.
To calculate this surface density, \citet{winn_background_2013}
queried the Besan\c con model
\citep{robin_synthetic_2003}  along a grid of galactic sight-lines,
and then converted to $I$-band surface brightnesses.
Fitting a smooth function to the results, \citet{winn_background_2013}
found
\begin{equation}
I\ {\rm mag\ arcsec}^{-2} =
    a_0 + a_1 \left(\frac{|b|}{40^\circ}\right)
    + a_2 \left(\frac{|l|}{180^\circ}\right)^{a_3},
\end{equation}
where the galactic longitude $l$ is measured from $-180^\circ$ to
$180^\circ$, and the empirical coefficients were found to be $a_0 =
18.9733$, $a_1=8.833$, $a_2=4.007$, and $a_3=0.805$.  This fit was
cautioned to be {\it very approximate}.  It is sensitive to the
threshold used to select ``unresolved'' stars, and likely no more
accurate than 0.5 mag on average.  In regions with exceptionally high
extinction ({\it e.g.}, star forming regions) it is expected to
systematic underestimate the background brightness by an even larger
degree.
Nonetheless, this model for the diffuse sky background seems
to agree reasonably well with the observed trend of standard deviation
versus stellar magnitude.

@@

\subsection{A Few Objects of Interest}
\label{subsec:identifying_variability}

\begin{figure}[!t]
	\gridline{\fig{tls_sde_vs_period_scatter.pdf}{0.45\textwidth}{}}
	\vspace{-0.8cm}
	\caption{
    Transiting planet search periodogram summary.
    Each point represents the TLS periodogram peak signal detection
    efficiency (SDE) and corresponding period from one light curve.
    Significance thresholds (orange lines) are empirically defined for
    the transiting planet search described in
    \S~\ref{subsec:identifying_variability}.  
    {\it Top.} Sector 6.  {\it Bottom.} Sector 7.
	}
	\label{fig:tlsresults}
\end{figure}

Below, we provide a few examples of how one might go about identifying
pulsating stars, strong stellar rotators, eclipsing binaries, and
transiting planets in the light curves.

\paragraph{Sinusoidal signals}
For pulsating stars and strong stellar rotators, the Lomb-Scargle
periodogram (CITE) is a tried-and-true discovery method.

We measured rotation periods for stars in X, Y clean cluster.

A figure is given here.

To identify an initial set of transiting planets, strong
stellar rotators, and eclipsing binaries, we performed a few steps of
post-processing on the light curves.  This processing was done
independently of the data release, since it was quite specific to our
own scientific interests.  The code used to do this additional
processing is also available
online\footnote{\url{github.com/lgbouma/cdips}, commit
\texttt{348eea7}.}.

%FIXME
%FIXME
%FIXME
%FIXME

\section{Discussion}
\label{sec: discussion}

We remind the reader that our goal in creating our target catalog was
completeness, rather than fidelity. The \citet{dias_proper_2014} stars
in particular were included if they were listed with membership
probability exceeding 50\%.  To create cleaner sub-samples, we advise
use of the \texttt{CDEXTCAT} header keyword, which can be used to
merge against the original source catalog to obtain the membership
probabilities claimed by the original catalog.

Despite our goal of completeness, some clusters may still be missing
members~--~the census of nearby coeval stellar populations is still
very much in flux ({\it e.g.}, \citealt{sim_open_2019};
\citealt{kounkel_untangling_2019}).  One particular area for concern in
the present work is sub-clusters of broader star-forming complexes,
for instance the Orion Nebula (M42; NGC 1976).  While it was observed
by TESS in Sector~6, searching our light curves for stars within 40
arcminutes, and 100 parsecs of the Orion Nebula's center yielded only
180 light curves, with 85 labelled members.  The Orion Nebula has
thousands of known members \citep{jones_proper_1988}.  However, due to
a combination of the spatially distributed nature of the broader
complex, as well as differential extinction, the automated methods of
the \citet{Kharchenko_et_al_2013} and \citet{dias_proper_2014}
assigned the Orion Nebula only 44 and 326 members, respectively.
\citet{cantat-gaudin_gaia_2018} explicitly excluded young star-forming
regions from their search, since the underlying assumption of their
clustering method (uniformity in the field star distribution) breaks
down in highly clustered star-forming regions.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}
\label{sec:conclusion}

%FIXME: paraphrase / improve all the below
In this study, we first collected an all-sky sample of about one million
candidate young stars brighter than $G_{\rm Rp}$ of 16.
82\% of the target star sample resides in a ``cluster'', a generic
term we adopted for open clusters, stellar associations, and moving
groups.
The remaining stars have photometric or astrometric indications of
their youth, and either reside on the pre-main-sequence or upper
main sequence.

>>>>

Each of the $\sim$3000 known star clusters of the Milky Way is a gift
to astrophysics, providing a sample of stars that vary widely in mass
but all have approximately the same age and composition.  Time-series
photometry of clusters has many applications. By measuring rotation
periods over a range of ages, we can study the angular momentum
evolution of stars and improve our ability to determine stellar ages
through gyrochronology \citep[{\it
e.g.},][]{skumanich_time_1972,barnes_color-period_2015,meibom_spin-down_2015,curtis_tess_2019}.
By measuring eccenticities as a function age, we can study the tidal
circularization of binaries
\citep{meibom_robust_2005,milliman_wiyn_2014,price-whelan_binary_2018}.
The detection of eclipsing binaries (EBs) can also lead to the precise
determination of the absolute dimensions of the stars and stringent
tests of stellar-evolutionary models
\citep{luhman_formation_2012,stassun_review_2014,kraus_mass-radius_2015}.
Finally, transiting exoplanets discovered in clusters can shed light
on the timescales for processes in planet formation, evolution, and
migration
\citep[][]{Fortney_et_al_2007,Mann_K2_33b_2016,David_et_al_2017}, as
well as on the effects of metallicity
\citep[][]{fischer_planet-metallicity_2005,petigura_metallicity_2018}.

@@

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{target_star_positions.png}
		%\gridline{\fig{target_star_cumulative_counts.pdf}{0.41\textwidth}{}}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    Target star positions (blue) and nominal TESS observing
    footprint (gray).  Target stars are either candidate members of
    clusters, or else have other youth indicators (see
    \S~\ref{sec:starselection}).  Most will be observed for one or two
    lunar months over the TESS Prime Mission.
    \label{fig:cdips_targets_positions}
	}
\end{figure*}

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		%\includegraphics[width=0.45\textwidth]{target_star_cumulative_counts.png}
		\gridline{\fig{target_star_cumulative_counts.pdf}{0.43\textwidth}{}}
		\vspace{-0.8cm}
		\gridline{\fig{target_star_hist_logt.pdf}{0.43\textwidth}{}}
		\vspace{-0.8cm}
		\gridline{\fig{target_star_reference_pie_chart.pdf}{0.43\textwidth}{}}
	\end{center}
	\vspace{-0.8cm}
	\caption{
		Target star statistics.
		{\it Top.} Cumulative counts as a function of Gaia $Rp$-band
		magnitude.  
		{\it Middle.} Histogram of target star ages, for the subset of
		stars with ages matched against \citet{Kharchenko_et_al_2013}.
		{\it Bottom.} Provenance of cluster membership.  Percentages are
		relative to $N_{\rm total}=1061446$ target stars. Symbols
		are as follows.
		D14 is \citet{dias_proper_2014}.
		K13 is \citet{Kharchenko_et_al_2013}.
		CG18 is \citet{cantat-gaudin_gaia_2018}.
		Z18 is \citet{zari_3d_2018}, with upper main sequence and
		pre-main-sequence samples sub-divided.
		``$\geq 2$'' indicates at least two authors reported a star as a
		candidate cluster member.
		%``Other'' refers to sources enumerated in \S~\ref{sec:starselection}.
		\label{fig:cdips_targets}
	}
\end{figure}

\begin{figure*}[!t]
	\gridline{\fig{mwscmatchstats.pdf}{0.83\textwidth}{}}
	\vspace{-1.1cm}
	\gridline{\fig{dias14matchstats.pdf}{0.83\textwidth}{}}
	\vspace{-0.8cm}
	\caption{
		{\it Top.} Quality diagnostics from cross-matching
		\cite{Kharchenko_et_al_2013} cluster members against Gaia-DR2.
		A histogram of the distances between matched stars is on the left; a
		histogram of the difference between the true $G$-band magnitude
		and that predicted from 2MASS photometry is in the middle; a scatter
		plot of the same magnitude difference as a function of $G$-band
		magnitude is on the right.
		{\it Bottom.} Same, but cross-matching \cite{dias_proper_2014}
		cluster members to Gaia-DR2.
	}
	\label{fig:xmatch_info}
\end{figure*}

@@

%FIXME: make table
The resulting CDIPS target star list is given in Table~\ref{tbl:cdips_targets}.
The cumulative distribution of target star brightnesses, as well as a
histogram of the ages, is shown in Figure~\ref{fig:cdips_targets}.
Relative to field stars, our target star sample is young, with a
typical age of 100$\,$Myr.

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.25\textwidth]{pipelineoverview.pdf}
	\end{center}
	\vspace{-0.2cm}
	\caption{
    Conceptual overview of photometric reduction pipeline.
    Details are given in \S~\ref{sec:method}.
	\label{fig:pipeline}
	}
\end{figure}

\begin{figure*}[!t]
    \begin{center}
        \leavevmode
        \includegraphics[width=0.93\textwidth]{stages_of_image_processing_good.png}
    \end{center}
    \vspace{-0.6cm}
    \caption{
        Stages of image processing for an image taken during the middle
        of an orbit.
        {\it Top right}. Calibrated image.
        {\it Top left}. Smooth background estimate.
        {\it Middle right}. Calibrated image minus its median pixel value.
        {\it Middle left}. Calibrated image minus smooth background.
        {\it Bottom left}. Registered difference image.
        {\it Bottom right}. Zoom of difference image.
        Each image is $(2048\times2048)$ pixels, except for the bottom-right 
        image, which is $(500\times500)$.
        All images except the top-right have the same color map.
        The sector, camera, and CCD are (6, 1, 2).
        \label{fig:stages_good}
    }
\end{figure*}

\begin{figure*}[!t]
    \begin{center}
        \leavevmode
        \includegraphics[width=0.93\textwidth]{stages_of_image_processing_bad.png}
    \end{center}
    \vspace{-0.6cm}
    \caption{
        Same sector, camera and CCD as Figure~\ref{fig:stages_good}, but for an image taken during
        perigee passage, when scattered light from the Earth is
        prominent.
        A number of systematic artifacts are present,
        including vertical ``straps'' and small-scale structure in scattered light
        patches.
        The quality of astrometric registration in the difference image is also
        worse, leading to larger residuals in the lower-right panel.
        \label{fig:stages_bad}
    }
\end{figure*}

@@

\begin{figure}[!t]
	\gridline{\fig{astromresidual_hist.pdf}{0.45\textwidth}{}}
	\vspace{-0.8cm}
	\gridline{\fig{astromresidual_quiver.pdf}{0.5\textwidth}{}}
  %\vspace{-0.8cm}
	%\gridline{\fig{astromresidual_apertures.pdf}{0.5\textwidth}{}}
	\vspace{-0.8cm}
    \caption{
		{\it Top.} Histogram of astrometric residual. The $x$-axis shows 
		the distance between the measured centroid positions of stars, 
		compared to the predicted positions from the WCS solution.
		{\it Bottom.} Vector plot of astrometric residual. Each arrow is 
		the vector from the measured to the projected star position. 
		Directions are correct, but lengths are 50 times their true size for 
		visualization purposes.
    The systematic error in the top-right corner is a typical
    problem generic to wide-field astrometry.
    The frame chosen for this plot is the photometric reference frame used 
    for Sector 6, Camera 1, CCD 1; we automatically 
    impose cutoffs on the median and $90^{\rm th}$ percentile of the 
    astrometric residual in order to ensure similar levels of astrometric 
    precision are maintained throughout the reduction.
	}
	\label{fig:astromresid}
\end{figure}

@@

With a kernel selected, and the convolution and subtraction performed,
we calculate the instrumental fluxes for each frame per
Equation~\ref{eq:ism_flux_measurement}.  We did this with three
different aperture sizes: for this work, circles of radii 1 pixel, 1.5
pixels, and 2.25 pixels.  These sizes were chosen to roughly span the
range of optimal aperture sizes for stars in our sample, as calculated
from the pre-flight \citet{Sullivan_et_al_2015} noise model.  Finally,
to convert from a list of flux measurements for each source on a frame
to a list of flux values at any given time, we used the
\texttt{fitsh} transposition tool \texttt{grcollect}.

@@

To determine the ``optimal'' number of principal components to use, we
performed a cross-validation analysis on the template stars using the
components derived both from PCA, as well as a separate factor
analysis.  As is typically the case when the noise variance is
different for each ``feature'' (each point in time), we found that
$k$-folding cross-validation using PCA failed to recover a plausible
number of components\footnote{See for example
\url{https://scikit-learn.org/stable/auto_examples/decomposition/plot_pca_vs_fa_model_selection.html}
 (2019/08/06).}.
However, the factor analysis typically maximized the cross-validation
score with anywhere from $10$ to $15$ components, which agreed with a
visual analysis of the number of PCA components past which overfitting
began.  We therefore used the maximum cross-validation score from
thefactor analysis as the number of principal components to use in
each light curve.  This number is documented in the \texttt{FITS}
header of each light curve.

@@

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{galacticcoords_cluster_field_star_positions.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    Positions of light curves from TESS Sectors 6 and 7 in galactic
    coordinates.  Black: $G_{\rm Rp}<13$ field stars.  Blue: $G_{\rm
    Rp}<16$ target stars.  Target stars are mostly near the galactic
    plane. The data for Sectors 6 and 7 cover about one-sixth of the
    galactic plane.
		\label{fig:lcgalactic}
	}
\end{figure*}

@@

\begin{figure}[!ht]
	\gridline{\fig{hrd_scat_all_CDIPS_LCs.pdf}{0.45\textwidth}{}}
	\vspace{-1.1cm}
	\gridline{\fig{hrd_scat_close_subset.pdf}{0.45\textwidth}{}}
	\vspace{-0.9cm}
	\caption{
    {\it Top.} HR diagram of CDIPS stars on silicon in this data
    release.  {\it Bottom.} HR diagram of close CDIPS stars on
    silicon. The wedge separating the pre-MS sample from the MS stars
    was discussed by \citet{zari_3d_2018}, who introduced it in order
    to avoid contamination by photometric binaries.
	}
	\label{fig:hrd}
\end{figure}

\begin{figure}[!t]
	\gridline{\fig{pm_scat_all_CDIPS_LCs.pdf}{0.45\textwidth}{}}
	\vspace{-0.9cm}
	\gridline{\fig{pm_scat_close_subset.pdf}{0.45\textwidth}{}}
	\vspace{-0.9cm}
	\caption{
		{\it Top.} Proper motions of CDIPS stars on silicon in this
		data release.  Many of the stars in the central ``blob'' are possible
		field-contaminants.
		{\it Bottom.} Proper motions of close CDIPS stars
		on silicon.
	}
	\label{fig:propermotions}
\end{figure}

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{IRM-PCA-TFA_rms_vs_mag.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    Standard deviation of CDIPS light curves as a function of catalog
    TESS-band magnitude.  Left-to-right are raw, PCA-detrended, and
    TFA-detrended light curves. Black points correspond to the minimum
    RMS across the available three aperture sizes.  The model (orange
    and gray lines) assumes aperture sizes reported by
    \citet{Sullivan_et_al_2015}, and the effective area from
    \citet{vanderspek_2018}.  The noise from unresolved background
    stars (dotted gray line) is a function of galactic latitude, and
    dominates over zodiacal light for faint stars near the galactic
    plane; the line shown assumes a sight-line towards the center of
    Sector 6, Camera 1 (further details are in
    \S~\ref{subsubsec:rmsvsmag}).
		\label{fig:rms_vs_mag}
	}
\end{figure*}

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.85\textwidth]{avg_acf.pdf}
	\end{center}
	\vspace{-0.7cm}
  \caption{
    Average autocorrelations of $10^4$ randomly selected light curves
    from each sector.  The medians at time lags spaced by one hour are
    shown for raw light curves (column name \texttt{IRM}) in gray, and
    for TFA-detrended light curves in black.  The gray bands display
    the 25$^{\rm th}$ to 75$^{\rm th}$ percentile range for each type
    of light curve.
  \label{fig:avg_acf}
	}
\end{figure*}

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{quilt_s6_s7.pdf}
	\end{center}
	\vspace{-0.8cm}
	\caption{
		Phased light curves for a few objects of interest.
		{\it Top row, left to right}:
		TOI~496 in Messier 48;
		TOI~625 orbiting a late A dwarf;
		and an eccentric EB in Bochum~5.
		{\it Middle row, left to right}:
		A detached EB in a 80~Myr old cluster;
		V684 Mon (a 10 Myr old detached EB);
		and a semi-detached EB in NGC 2548.
		{\it Bottom row, left to right}:
		Spotted rotator in NGC 2184;
		a pulsator or perhaps EB flagged by \citet{zari_3d_2018} as a pre-MS 
		star;
		and a quasi-periodic pulsator, also with a pre-MS host.
		Gaia source identifiers are given in the text.
	\label{fig:quilt}
	}
\end{figure*}

\subsection{Light curve statistics}
\label{subsec:lcstatistics}

@@

The relevant quantity needed to calculate the integrated 
photon counts from faint sources
is  $N(<m,l,b)$ --- the number of stars per square arcsecond
brighter than magnitude $m$, along a line of sight with galactic
longitude and latitude $(l,b)$.
To calculate this surface density, \citet{winn_background_2013}
queried the Besan\c con model
\citep{robin_synthetic_2003}  along a grid of galactic sight-lines,
and then converted to $I$-band surface brightnesses.
Fitting a smooth function to the results, \citet{winn_background_2013}
found
\begin{equation}
I\ {\rm mag\ arcsec}^{-2} =
    a_0 + a_1 \left(\frac{|b|}{40^\circ}\right)
    + a_2 \left(\frac{|l|}{180^\circ}\right)^{a_3},
\end{equation}
where the galactic longitude $l$ is measured from $-180^\circ$ to
$180^\circ$, and the empirical coefficients were found to be $a_0 =
18.9733$, $a_1=8.833$, $a_2=4.007$, and $a_3=0.805$.  The fit was
cautioned to be {\it very approximate}.  It is sensitive to the
threshold used to select ``unresolved'' stars, and likely no more
accurate than 0.5 mag on average.  In regions with exceptionally high
extinction ({\it e.g.}, star forming regions) it is expected to
systematic underestimate the background brightness by an even larger
degree.
Nonetheless, this model for the diffuse sky background seems
to agree reasonably well with the observed trend of standard deviation
versus stellar magnitude.

@@

\subsection{Exploring the variability}
\label{subsec:identifying_variability}

The light curves provide an opportunity to study many types of
variables, including pulsating stars, rotators, eclipsing binaries,
and transiting planets.
A few hand-picked examples are shown in Figure~\ref{fig:quilt}.
The sources\footnote{
	Top-left to bottom-right:
	3064530810048196352, 
	3080104185367102592, 
	3027361888196408832,
	3125738423345810048,
	3326715714242517248,
	3064487241899832832,
	3024952755135530496,
	2949587413510194688, 
	5274902193830445312 
} were identified by calculating Lomb-Scargle and transit-least
squares periodograms for a subset of the light curves, and inspecting
the peaks with the greatest power
\citep{lomb_1976,scargle_studies_1982,kovacs_box-fitting_2002,vanderplas_periodograms_2015,hippke_TLS_2019}.
We calculated the periodograms using
\texttt{astrobase}.
Our search was extremely cursory~--~a detailed search for transiting
exoplanets will be the subject of future work.
To make the figure, we used the ``PCA2'' light curve for each
star, for simplicity's sake.
To remove outliers, we omitted
data points within 6 hours of the beginning or end of each orbit.
No additional detrending was performed.

The top row of Figure~\ref{fig:quilt} shows two TESS objects of
interest, and an eccentric eclipsing binary.  TOI~496 is a member of M~48 
(NGC~2548,
\citealt{gaia_collaboration_gaia_2018,cantat-gaudin_gaia_2018}), a
$\sim$500 Myr old open cluster \citep{Kharchenko_et_al_2013}.  The
phase variations suggest that it is an eclipsing binary.  TOI~625 is a
potential hot Jupiter orbiting an upper main sequence star, and was
included as a CDIPS target through the \citet{zari_3d_2018}
catalog.  The eccentric EB was claimed by \citet{dias_proper_2014} to
be a member of the $\sim$50 Myr Bochum~5 cluster.  This EB is also of
note because its TFA light curve heavily whitens the out-of-eclipse
signal, leaving an eclipse signal would could be mistaken for a planet 
candidate.  The important
check for potential users of the light curves is of course to consider
light curves with different types of detrending, to prevent these types of
misinterpretations.

The middle row of Figure~\ref{fig:quilt} shows a few more interesting
eclipsing binaries.  On the left is a detached EB exhibiting large
out-of-eclipse modulations in a $\sim$80~Myr
open cluster (``vdBergh 85'', \citealt{Kharchenko_et_al_2013}).
In the middle we have V684 Mon, a well-known $\sim$10~Myr old
detached EB in the very young star-forming region NGC 2264.
Finally on the right, we have a semi-detached EB in Messier~48.

The bottom row of Figure~\ref{fig:quilt} gives a few examples
of rotators and pulsators.  On the left, a spotted rotator in the
$\sim$400 Myr NGC~2184 \citep{cantat-gaudin_gaia_2018}.
In the middle, we have a pulsator, or perhaps EB flagged by
\citet{zari_3d_2018} as a pre-MS star.
Finally on the right is a quasi-periodic pulsator, or perhaps rotator,
also with a pre-MS host.

The overall point is that a great number of systems with known ages
should be identifiable from the data at their current level of
preparation.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion \& Conclusion}
\label{sec:conclusion}

In this study, we first collected an all-sky sample of about one
million stars brighter than $G_{\rm Rp}$ of 16.  82\%
of this target star sample are candidate ``cluster'' members, 
where we use the generic ``cluster'' to refer to 
open clusters, stellar associations, and moving groups.
The remaining stars had photometric or astrometric indications of
their youth, and either reside on the pre-main-sequence or upper main
sequence.
